\begin{changemargin}{-0.2cm}{-0.2cm}
\noindent
First and foremost I would like to thank my supervisor, J{\"o}rg Liesen.
He was responsible for introducing me to the fascinating area of mathematics that gave rise to this work (and in a deeper sense to the entire universe of mathematics), for which I will always be grateful. I owe the completion of this thesis to his guidance, wisdom and quasi-infinite patience over the past six years. Given his support, inspiring discussions, great ideas, and a total freedom of research it has been a pleasure to work with, and learn important values and ideals from such a wholesome person and exceptional scientist.

Following closely behind in importance I would like to thank Evelyn Schubert,
for teaching me all the things about life that one can not learn in the books. For sharing her love with me throughout these years, helping me grow and become the person that I am today. I can only feel a sense of infinite gratitude for your comfort, patience and~love.\linebreak
\indent I will also always feel a deep sense of gratitude for my colleagues at the Institute for Mathematics of the TU Berlin, my collaborators, supervisors, mentors, co-authors, and referees from other institutions: Reinhard Nabben, Daniel Szyld, Petr Tich{\'y}, Michele Benzi, Kees Vuik, Volker Mehrmann, Mikhail Karow, Oliver S{\`e}te, Jan Zur, Ren{\'e} Kehl, Candan G{\"u}d{\"u}c{\"u} and everyone who shared insightful and great discussions with me throughout these years! Thank you for your sympathy, and your help. I will always remember the endless cups of coffee (\emph{yerba mate} in my case) that we shared together!

I would also like to thank the institutions who have sustained my research throughout my time as a doctoral student: The Technische Universit\"at Berlin, the Berlin Mathematical School, the Berlin Einstein Center for Mathematics, The Berlin Mathematics Research Center MATH+, the ``Deutscher Akademischer Austauschdienst'' (DAAD) in Germany, and the ``Consejo Nacional de Ciencia y Tecnolog\'ia'' (CONACYT) in Mexico. This work could not have been achieved without their generous support.

% It is also important to mention the people who helped keep most of the administrative tasks of the university away from my focus: Annett Gillmeister, Kerstin Ullrich, Sven Gr{\"o}tke, Annika Preu\ss, Tanja Fagel, Shirley Sutherland-Figini, Forough Sodoudi, and Nadja Wisniewski. Thank you for your support and your help. Your work and dedication allowed me to concentrate on my research without too many distractions.

Furthermore, I deeply wish to thank my close personal friends who include, but
are not limited to: Dominik Dreiner, Maximillian-Johannes-Peter Geisthardt, Luis Garc{\'i}a Ramos, Andr{\'e} Gaul, Pabla Fiorella Perez, Alexander Hamel, Christine Eberhardt, Judith Wolff, H{\'e}ctor Andrade Loarca, Tobias Wieland, Rodrigo Chavezmontes Jato, and everyone else who kept close to me even from the other side of the ocean. Your friendship kept me going through the good and the bad times, where I needed it the most. Thank you for being there.

Lastly, but most importantly than anybody else, I would like to thank my family. I will be eternally grateful to my mother, Raquel Serur, and father, Bolivar Echeverr{\'i}a, to whom I owe my life. I thank them for the love, dedication, support and education that was given to me from the day I was born. And to Alberto Echeverr{\'i}a, my favorite person on this Earth, thank you for being my brother, both in flesh and soul. %I love you.

\medskip

To everyone else who I have forgotten to mention: Thank you!
% This thesis would not have been written without you!\textcolor{white}{<3}
\end{changemargin}
\afterpage{\blankpage}
